\documentclass[11pt,fleqn]{article}

\setlength {\topmargin} {-.15in}
\setlength {\textheight} {8.6in}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}

\renewcommand{\labelenumi}{\theenumi.}
\renewcommand{\labelenumii}{\theenumii.}
\renewcommand{\labelenumiii}{\theenumiii.}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\bsp}{\begin{sloppypar}}
\newcommand{\esp}{\end{sloppypar}}
\newcommand{\mname}[1]{\mbox{\sf #1}}
\newcommand{\sB}{\mbox{$\cal B$}}
\newcommand{\sC}{\mbox{$\cal C$}}
\newcommand{\sE}{\mbox{$\cal E$}}
\newcommand{\sF}{\mbox{$\cal F$}}
\newcommand{\sL}{\mbox{$\cal L$}}
\newcommand{\sM}{\mbox{$\cal M$}}
\newcommand{\sP}{\mbox{$\cal P$}}
\newcommand{\sV}{\mbox{$\cal V$}}
\newcommand{\set}[1]{{\{ #1 \}}}
\newcommand{\Neg}{\neg} 
\ifdefined \And 
\renewcommand{\And}{\wedge}
\else
\newcommand{\And}{\wedge}
\fi
\newcommand{\Or}{\vee}
\newcommand{\Implies}{\Rightarrow}
\newcommand{\Iff}{\Leftrightarrow}
\newcommand{\Forall}{\forall}
\newcommand{\ForallApp}{\forall\,}
\newcommand{\Forsome}{\exists}
\newcommand{\ForsomeApp}{\exists\,}
\newcommand{\mdot}{\mathrel.}

\begin{document}

\begin{center}

  {\large \textbf{COMPSCI/SFWRENG 2FA3}}\\[2mm]
  {\large \textbf{Discrete Mathematics with Applications II}}\\[2mm]
  {\large \textbf{Winter 2021}}\\[8mm]
  {\huge \textbf{Extra Credit Assignment 4}}\\[6mm]
  {\large \textbf{Dr.~William M. Farmer and Dr.~Mehrnoosh Askarpour}}\\[2mm]
  {\large \textbf{McMaster University}}\\[6mm]
  {\large Revised: March 19, 2021}

\end{center}

\medskip

Extra Credit Assignment 4 consists of paper that describes the design
of a text searching program.  Your paper must be written in LaTeX.

\bsp
Please submit Extra Credit Assignment~4 as two files,
\texttt{EC\_Assignment\_4\_\emph{YourMacID}.tex} and
\texttt{EC\_Assignment\_4\_\emph{YourMacID}.pdf}, to the Extra Credit
Assignment~4 folder on Avenue under Assessments/Assignments.
\texttt{\emph{YourMacID}} must be your personal MacID (written without
capitalization).  The \texttt{EC\_Assignment\_4\_\emph{YourMacID}.tex}
file is a copy of the LaTeX source file for this assignment
(\texttt{EC\_Assignment\_4.tex} found on Avenue under
Contents/Assignments) with your solution entered after the problem.
The \texttt{EC\_Assignment\_4\_\emph{YourMacID}.pdf} is the PDF output
produced by executing
\esp

\begin{itemize}

  \item[] \texttt{pdflatex EC\_Assignment\_4\_\emph{YourMacID}}

\end{itemize}

This assignment is due \textbf{Sunday, April 4, 2021 before
  midnight.}  You are allow to submit the assignment multiple times,
but only the last submission will be marked.  \textbf{Late submissions
  and files that are not named exactly as specified above will not be
  accepted!}  It is suggested that you submit your preliminary
\texttt{EC\_Assignment\_4\_\emph{YourMacID}.tex} and
\texttt{EC\_Assignment\_4\_\emph{YourMacID}.pdf} files well before the
deadline so that your mark is not zero if, e.g., your computer fails
at 11:50 PM on April 4.

\textbf{Although you are allowed to receive help from the
  instructional staff and other students, your submission must be your
  own work.  Copying will be treated as academic dishonesty! If any of
  the ideas used in your submission were obtained from other students
  or sources outside of the lectures and tutorials, you must
  acknowledge where or from whom these ideas were obtained.}

\newpage

\subsection*{Extra Credit Problem \textbf{[2 bonus points]}}

Construct an NPDA for the complement\footnote{The complement of language L, defined over $\Sigma$ is the set of all strings in $\Sigma^*$ that are not in L.} of $L = \{ ww \mid w \in \{a,b\}^*\}$.
\\

\bigskip

\noindent
\textcolor{blue}{\textbf{Aidan Mariglia, mariglia, 04/04/21}}

\bigskip

\noindent

$L = w \in \{a, b\}^* - \{ww | w \in \{a, b\}^* \}$\\

$M = (Q, \Sigma, \Gamma, \delta, s, \bot, F)$\\
$Q = \{q_1, q_2, f\}$\\
$F = \{f\}$\\
$\Sigma = \{a, b\}$\\
$\Gamma = \Sigma \cup \{\bot\}$\\
$\delta = $\\
\bi
  \item $((q_1, a, \bot),(q_1, a\bot))$
  \item $((q_1, a, a),(q_1, aa))$
  \item $((q_1, b, \bot),(q_1, b\bot))$
  \item $((q_1, b, b),(q_1, bb))$
\ei

\end{document}


